Forecasting interrupted time series

### 2023-07-29 fits.qmd
add over sampling and ensemble

>>>>

## Over sampling (weighting)

Oversampling is a technique used in machine learning to address class imbalance within a dataset. In this context, the goal is to ensure that the model is more influenced by the patterns observed before the disruption period while still accounting for the observations during the disruption period.

Using this weighting approach, we can leverage the insights from the pre-disruptive period while still accounting for the disruptive period's influence. It allows the model to better capture the underlying patterns of the time series data, considering both periods, and potentially producing more accurate forecasts.

Advantages:

Preserves pre-event patterns: By assigning higher weights to the pre-disruption time series data, the model is encouraged to focus more on the patterns observed before the disruptive event. This can be beneficial in capturing the underlying dynamics of the time series that might be essential for accurate forecasting in the post-disruption era.

Robustness to disruption impact: The weighting approach allows the model to still take the disruption period into account, even if it's considered less influential. This ensures that the model is not completely blind to the disruption's effects and can adapt to changes or shifts in the time series caused by the event.

Easy to Implement: ??

Interpretability?:

Disadvantages:

## Ensemble models
